Sketch of DP - Bayesian Inference

### 2018-07-14 main-sketch.tex
abstract

\begin{abstract}
Differential privacy mechanisms now are widely used in different algorithms. Accuracy of these mechanisms is usually measured by $l_1$ norm regardless what mechanisms are based on. We observed that when mechanism protect privacy according to a certain measurement, mechanism' accuracy behavior will be better than when protect according to other measurements. This observation prompt us to design a new mechanism under Hellinger distance measurement based on basic exponential named exponential mechanism with smooth sensitivity. In this algorithm we add noise to data according to the Hellinger distance. We proved in experiments that we can have a better accuracy than Laplace mechanism which adding noise based on $l_1$ norm under Hellinger measurement.
\end{abstract}

@@

We are studying the Bayesian inference in Beta-Bernoulli systems. So this part we will technically describe our problem under Beta-Bernoulli systems of Bayesian inference. Suppose $\pi(\xis)$ is our prior belief about some parameters or latent variables $\xis$. By using a group of observed data $\textbf{x}$ sizing $n$, the likelihood of this group of data is $Pr(\textbf{x} | \xis)$, we produce a posterior distribution:
\begin{equation*}
Pr(\xis | \textbf{x}) = \frac{Pr(\textbf{x} | \xis) \pi(\xis)}{Pr(\textbf{x})},
\end{equation*}
denoted as $\bysinfer(\textbf{x},\pi(\xis))$ taking an observed data set $\textbf{x} \in \mathcal{X}^n$ (i.e., $\{0,1\}^n$) and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

@@

The posterior belief about parameters $\xis$ is inferred from the group of sensitive data. Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ themselves can relieve a lot of information about sensitive data. So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it. Then it will be better if we can use a distance over two distributions to measure the accuracy than a distance over values when we are protecting a distribution, for instance, we are using Hellinger distance in our paper. When we measure the accuracy between true posterior and protected posterior using Hellinger distance, it would be better we can have a protection mechanism based on Hellinger distance. However, current mechanisms are mainly based on $l_1$ norm by Laplace mechanism \cite{zhang2016differential}. That's why we design our exponential mechanism over Hellinger distance to protect the whole posterior distribution.

>>>>

\begin{abstract}

  Bayesian inference is a statistical method which allows to derive
  a \emph{posterior} distribution over a parameter, 
  starting from a \emph{prior} distribution and observed data.
  Many works have focused on making this
  process differentially private adding noise on the parameters
  representing the distributions\todo{cite?}.
  % Also,  the sensitivity 
  % was computed w.r.t. a numeric norm over the space of the numeric parameters
  % characterizing the output distribution.
  Also, the accuracy was measured
  using metrics on the space of the numeric parameters representing the
  posterior distribution, e.g. $\ell_1$-norm \todo{cite}.

  We designed a new mechanism for differentially private Bayesian inference
  where the noise is proportional to a smooth sensitivity computed w.r.t a metric
  on probability distributions; we also measured the accuracy of the process
  by using a metric over probability measures.
  We compared the accuracy of this approach with the one based on $\ell_1$-norms.
  Experimental results show that in some situations the former outperforms the latter.

\end{abstract}

@@

We are studying the Bayesian inference in Beta-Bernoulli systems. So this part we will technically describe our problem under Beta-Bernoulli Bayesian inference systems. Suppose $\pi(\xis)$ is our prior belief about some parameters or latent variables $\xis$. By using a group of observed data $\textbf{x}$ sizing $n$, the likelihood of this group of data is $Pr(\textbf{x} | \xis)$, we produce a posterior distribution:
\begin{equation*}
Pr(\xis | \textbf{x}) = \frac{Pr(\textbf{x} | \xis) \pi(\xis)}{Pr(\textbf{x})},
\end{equation*}
denoted as $\bysinfer(\textbf{x},\pi(\xis))$ taking an observed data set $\textbf{x} \in \mathcal{X}^n$ (i.e., $\{0,1\}^n$) and a prior distribution $\pi(\xis)$ as input, outputting a posterior distribution of the parameter $\alphas$. For conciseness, when prior is given, we use $\bysinfer(x)$. $n$ is the size of the observed data size.

@@

The sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$ rather than a sample drew from it.  we use mechanisms to protect the inference results to get private posteriors: $\dirichlet(\alphas^*)$. When we measure the distance between true posterior and protected posterior, we will have different result on $l_1$ norm and Hellinger distance. We believe that if the protected posterior is produced based on Hellinger distance, it will have a better accuracy than produced based on the $l_1$ norm.
